%-------------------------
% Resume in Latex
% Author : Riviera Sperduto
% Based off of: https://github.com/sb2nov/resume and jake's Resume: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Anonymous Person} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{schoolemail@school.edu}} $|$
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/yourprofileURL}} $|$
    \href{https://github.com/...}{\underline{github.com/yourprofileURL}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Temple University}{Philadelphia, PA}
      {Bachelor of Science in Computer Science}{Aug. 2023 -- May 2025}
    \resumeSubheading
      {Community College of Philadelphia}{Philadelphia, PA}
      {Associates of Science in Mathematics}{Aug. 2021 -- May 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Information Technology Intern}{September 2024 -- December 2024}
      {SNIPES USA}{Bensalem, PA}
      \resumeItemListStart
        \resumeItem{Developed and tested Python programs, including tools to automate SDWAN updates and network traffic analysis, improving efficiency and generating organized reports.}
        \resumeItem{Fixed a critical test for the staging website to ensure functionality by identifying broken links across all pages.}
        \resumeItem{Shadowed a System Administrator to learn VM creation in Azure, Microsoft Active Directory, and other Azure tools.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Student Worker/Intern}{October 2023 -- Present}
      {Temple University}{Philadelphia, PA}
      \resumeItemListStart
        \resumeItem{Created and optimized programs to automate data verification processes, improving runtime efficiency and doubling productivity.}
        \resumeItem{Deciphered SQL files and documentation to help the team understand backend functionality and query operations.}
        \resumeItem{Designed and documented automation programs, enabling team members to recreate and implement them independently.}
    \resumeItemListEnd

    \resumeSubheading
      {Volunteer}{March 2020 -- Present}
      {Whitemarsh Art Center}{Conshohocken, PA}
      \resumeItemListStart
        %\emph is italics
        %\resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
        \resumeItem{Aided with the transition to MailChimp by cleaning and uploading email lists and assigning customer
tags/audiences.}
        \resumeItem{Allowed the ability to specifically target specific groups for different advertisements}
        \resumeItem{Manufactured memes for the purpose of advertising classes on their social media platforms}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{BestNotes} $|$ \emph{Python, Qt Core, Pyside 6}}{October 2024 -- December 2024}
          \resumeItemListStart
            \resumeItem{Contributed to a capstone project to develop a free, open-source note-taking application using Python, PySide6, and related libraries.}
            \resumeItem{Designed a moveable toolbar for app functionality and implemented customizable eraser features for enhanced user interaction.}
            \resumeItem{Created and executed tests to ensure application reliability and measured code coverage.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Projectile Launcher Rework} $|$ \emph{Lua, YAML, JSON, RedScript}}{December 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Created a mod for the hit video game Cyberpunk 2077 that has over 45k individual downloads}
            \resumeItem{Modified game mechanics and developed new variants, attachments, and ammo for the projectile launcher using multiple programming languages.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Books and More! Database} $|$ \emph{MySQL, Maria DB}}{March 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Designed and implemented an RDBMS for "Books and More!" bookstore, managing inventory, customers, sales, and vendors with detailed data modeling and SQL scripts.}
            \resumeItem{Developed custom triggers to bypass a MySQL bug, ensuring referential integrity and reliable audit tracking.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Kotlin, Java, C/C++, SQL (MySQL \& Postgres), JavaScript, HTML/CSS, YAML, Lua, RedScript} \\
     \textbf{Frameworks}{: Testim.io, Microsoft Active Directory} \\
     \textbf{Developer Tools}{: Git/GitHub, Docker, Microsoft Azure, VS Code, Visual Studio, PyCharm, IntelliJ, MariaDB, Dependency Track, Microsoft Power Automate} \\
     \textbf{Libraries}{: Qt Core, Pyside6, Meraki, GUIZero}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
